A Connection Between Star Formation Rate and Dark Matter Halos at $Z\sim6$ In 2013 Planck Cosmology.

### 2014-06-30 paper/fitting_model.tex
adding references
LF model

\section{The Fitting Model}
The model links dark matter and U-luminosity by a four parameter function.
For each galaxy we have the luminosity:
  \begin{equation}
  L = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
		   + \left( \frac{M}{M_0}\right)^{\gamma} 
               \right]^{-1}
  \end{equation}
where $M$ is the hosting DMH mass, $L_{0}$ is a normalization constant, $M_0$
is the critical mass where the luminosity function has a slope change, 
$\beta$ and $\gamma$ are the slopes.
This relation can reproduce the luminosity function with best agreement than the classical Schechter function wich works good for low redshift galaxies.

This equation has a similar fashion to the mass to light relation \citep{vandenbosch03} and the mean relation between stellar mas of a galaxy and the mas of its halo used by \cite{moster10}.

>>>>

\subsection{The Luminosity Model}

In this model we have made two assumptions:
\begin{enumerate}
 \item Each halo in the catalog hosts one galaxy. There are not empty
halos, also none of halos has two or more galaxies.
 \item The UV luminosity of each galaxy is function of one variable: the mass of
the DMH in wich is located.
\end{enumerate}

The simplest relation we can have is a powerlaw:
 \begin{equation}
  L = L_0 M^\alpha
 \end{equation}
but has not well agreement with observed luminosity functions.

A better model is a four parameter function. Each galaxy has a luminosity given
by:
  \begin{equation}
  L = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
		   + \left( \frac{M}{M_0}\right)^{\gamma} 
               \right]^{-1}
  \end{equation}
where $M$ is the hosting DMH mass, $L_{0}$ is a normalization constant, $M_0$
is the critical mass where the luminosity function has a slope change, 
$\beta$ and $\gamma$ are the slopes. This equation has a similar fashion to the
mass to light relation \citep{vandenbosch03} and the mean relation between
stellar mas of a galaxy and the mas of its halo used by \cite{moster10}.

There are more complex models\citep{lee09} that includes a random behavior:
galaxies has not synchronization on the beginning of star forming stage, also
this stage may be time limited. This is called duty cycle. It is probable to
have in the observations some invisible galaxies in the UV continuum due their
duty cycle may has not started as well it may ended. Also may be present a
normal distribution of the luminosity around the expected values.

### 2014-06-30 paper/star_formation_rate.tex
SFR, Fitting Model, The_Bibliography
LF model

\section{Star Formation Rate}

On the study of far galaxies individual stellar spectrum is unresolved, is not 
possible to make a detailed census of the galaxy popullation. Only is possible 
to get information from the whole stellar population, an integrated spectrum.

Kennicutt pruposed a method in wich a linear relation between luminosity and 
SFR can be assumed. This model allows to estimate the young stars fraction and 
the mean SFR over periods of $10^8 - 10^9 \textrm{yr}$. The luminosity in the 
modfel, comes from the UV and the FIR broadband, also from speciffic 
recombination lines.

@@

@@

>>>>

\subsection{Star Formation Rate}

The age of a star can be estimated by analyzing its spectrum. But when far
galaxies are studied, individual stars can not be resolved. Is not 
possible to make a detailed census of the galaxy popullation. Only is possible 
to get information from the whole stellar population, an integrated spectrum.

Kennicutt pruposed a method in wich a linear relation between SFR and
luminosity in specific wavelength ranges can be assumed. This model allows to
estimate the young stars fraction and the mean SFR over periods of $10^8 - 10^9
\textrm{yr}$. The luminosity in the model, comes from the UV and the FIR
broadband, also from speciffic recombination lines.

@@

The star forming rate will be:
  \begin{equation}
  SFR = k \times L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
		   + \left( \frac{M}{M_0}\right)^{\gamma} 
               \right]^{-1}
  \end{equation}

@@

DUST EXTINTION ALSO STUDIED by 002-TACCHELLA-A Physical Model for ---
